% LaTeX file for resume 
% This file uses resume document class (res.cls)

\documentclass{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}  % uses hyberlinks
\hypersetup{hidelinks}
\usepackage{geometry}
\geometry{left=1.05cm,right=2.55cm,top=1.5cm,bottom=1cm} 
%\usepackage{CJK}

\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{Zixiang Wang\\[8pt]}     % \\[12pt] adds a blank
                        % line after name  

\address{
    (315)-965-6606 $|$
    \href{mailto:wangtzuhsiang@gmail.com}{wangtzuhsiang@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/zixiangwang}{LinkedIn.com/in/zixiangwang/} $|$ 
    \href{https://github.com/DolorHunter}{GitHub.com/DolorHunter} $|$ 
    \href{https://leetcode.com/wubai500/}{LeetCode Top6\%}
}

\begin{resume}
\vspace{-13pt}
\hspace{-0.55in}
\noindent\rule[0.25\baselineskip]{19.36cm}{1.2pt}    
\vspace{-20pt}  

\vspace{-0.1in}
\section{EDUCATION} 
    \vspace{0.00in}	 
    \begin{tabbing}
    \hspace{3.49in}\= \hspace{2in}\= \kill % set up two tab positions
    {\bf Syracuse University} 
        \>Syracuse, NY \` Aug 2021 - May 2023
    \end{tabbing}\vspace{-18.5pt}      % suppress blank line after tabbing
    Master of Science - MS, Computer Science
    \hspace*{\fill} GPA: 3.5/4.0 (Core)

    \vspace{-0.1in}
    \begin{tabbing}
    \hspace{3.49in}\= \hspace{2in}\= \kill % set up two tab positions
    {\bf Hefei University of Technology } 
        
        %\hspace{-0.1in}\begin{CJK}{UTF8}{kai} {\bf 「合肥工業大學」 } \end{CJK} 
        \>Hefei, Anhui, China \` Sep 2017 - Jun 2021
    \end{tabbing}\vspace{-18.5pt}      % suppress blank line after tabbing
    Bachelor of Science - BS, Computer Science
        %\> \hspace{300pt}GPA: 3.5/4.0 (Core)

\vspace{-8pt}
\hspace{-0.55in}
\noindent\rule[0.25\baselineskip]{19.36cm}{0.5pt}    

\vspace{-0.2in}
\section{EXPERIENCE}
    % first experience
    \vspace{0.00in}	
    \begin{tabbing}
    \hspace{1.5in}\= \hspace{2in}\= \hspace{1.6in}\= \kill % set up two tab positions
    {\bf Google} \> {\bf Software Engineer}  \>  
                                    Mountain View, CA    \` Nov 2024 - Present\\
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    % descriptions
    \vspace{+0.1in}
    \begin{itemize} \itemsep 1.5pt %reduce space between items
    \item Designed and implemented {\bf backend infrastructure} for the next-generation Google Analytics and Ads 
        platform, working with the top x largest datasets in the company.
    \item Developed scalable {\bf pipelines} for {\bf real-time} and {\bf streaming} {\bf data processing}, 
        utilizing {\bf C++} to ensure high throughput and low latency for {\bf big data} workflows.
    \item Developed monitoring tools using {\bf Python} to ensure the reliability and performance of data pipelines.
    \item Built robust {\bf infrastructure} to support advanced modeling and prediction capabilities, 
        enabling data-driven insights and informed decision-making.
    \item Partnered with cross-functional teams to deliver actionable insights and decision-making data through 
        a highly scalable and efficient infrastructure.
    \end{itemize}


    % second experience
    \vspace{0.00in}	
    \begin{tabbing}
    \hspace{2.8in}\= \hspace{1.8in}\= \hspace{1.2in}\= \kill % set up two tab positions
    {\bf Microsoft (Vendor, via iSoftStone)} \> {\bf Software Engineer}  \>  
                                    Remote    \` Jul 2023 - Oct 2024\\
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    % descriptions
    \vspace{+0.1in}
    \begin{itemize} \itemsep 1.5pt %reduce space between items
    \item Developed and implemented web components for {\bf Microsoft's OneCloud} team, using {\bf JavaScript}, 
        {\bf CSS}, {\bf HTML}, and {\bf Figma}. Additionally, contributed to the ReimagineUI library 
        through the creation of new components, sample use cases, and updating outdated documents.
    \item Deployed UI components to {\bf Adobe Experience Manager (AEM)}, featuring updates to the core framework, 
        policy, component templates, and dialogs using expertise in {\bf Java}, {\bf C\#}, and {\bf XML}.
    \item Pioneered the development of Accessibility AI tools using {\bf Python}. 
        Implemented {\bf Machine Learning} and {\bf NLP} models to generate data insights using OpenAI and AltTextAI.
        Enhanced implementation with {\bf multi-threading}, leading to a 300\% increase in average efficiency.
    \item Scripted in {\bf Python} for automated data validation and narrative generation across diverse sources.
    \item Constructed {\bf CI/CD} pipelines on {\bf GitHub} to automate deployment to 
        {\bf Microsoft Azure Cloud} services, including {\bf Function App} and {\bf Static Web Apps}.
    \item Utilized version control with {\bf Git}, and employed {\bf Agile} 
        development methodologies within {\bf Azure DevOps}.
    \end{itemize}


    % third experience
    \vspace{-0.05in}	
    \begin{tabbing}
    \hspace{1.5in}\= \hspace{2.5in}\= \hspace{1.6in}\= \kill % set up two tab positions
        {\bf iSoftStone} \> {\bf Software Engineer Intern}  \>  
                                    Shenzhen, China   \` Jul 2020 - Sep 2020\\
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    % descriptions
    \vspace{+0.1in}
    \begin{itemize} \itemsep 1.5pt %reduce space between items
        \item Developed robust {\bf back-end APIs} for {\bf data visualization} 
            platform named {\bf A-Data}.
        \item Designed and developed {\bf RESTful API} for authentication and 
                data portal module using {\bf Spring} and {\bf Java}.
        \item Applied {\bf Asynchronous Programming} to create threads, effectively boosting overall performance.
        \item Devised a storage system utilizing {\bf MySQL} and {\bf XML}, ensuring seamless data management.
        \item Leveraged {\bf Navicat} for proficient database management and {\bf Postman} for meticulous API testing.
        \item Tracked changes with {\bf SVN} and executed project deployment on servers via {\bf Jenkins}.
                on server.
    \end{itemize}

\vspace{+0.05in}

\vspace{-8pt}
\hspace{-0.55in}
\noindent\rule[0.25\baselineskip]{19.36cm}{0.5pt}    
        
% \vspace{-0.2in}
% \section{PROJECT}

%     % first project
%     \vspace{-0.05in}	 
%     \begin{tabbing}
%     \hspace{2.3in}\= \hspace{3.45in}\= \kill % set up two tab positions
%     \href{https://github.com/DolorHunter/AutoTBOXDataSystem}{\bf Auto TBOX Data System}  \> 
%                 Spring, Java, React, JavaScript, Python, MySQL \> 
% 				Oct 2020 - June 2021
% 				\\
%     \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing \
%     % descriptions
%     \vspace{+0.1in}
%     \begin{itemize} \itemsep 1.5pt %reduce space between items
%         \item Developed {\bf full-stack} website for data visualization of vehicle faults for a {\bf Fortune 500} company.
%         \item Created RESTful APIs for 12 modules using {\bf Spring Boot} and {\bf Java}, 
%             contributing to robust system design.
%         \item Constructed websites using {\bf React}, {\bf JavaScript}, {\bf HTML}, and {\bf CSS} 
%             to visualize real-time statistics and distributions.    
%         \item Set up {\bf MySQL} and managed database using {\bf Navicat}, 
%             performed {\bf unit test} with {\bf Postman}.
%         \item Synthesized and scrutinized vehicle fault data, fetched via an API interface, utilizing {\bf Python}.
%     \end{itemize}

      
% \vspace{-2pt}
% \hspace{-0.65in}
% \noindent\rule[0.25\baselineskip]{19.36cm}{0.5pt}    

\vspace{-0.2in}
\section{TECHNICAL SKILLS}  
    \vspace{+0.1in}
    \hspace{-0.12in} 
    \begin{tabular}{l p{5.5in}}
    \rule{0in}{0.2in}
    {\sl Languages:} & Python, C/C++, Java, C\#, Kotlin, SQL, HTML, CSS, JavaScript, XML \\
    \rule{0in}{0.2in}
    {\sl Frameworks:} & Spring Boot, Django, React, AWS, Microsoft Azure, Azure DevOps, GCP, Firebase, 
                        Jenkins, GitHub Actions, Docker, CI/CD, Android, PyTorch, Nginx, Qt, Linux, Git
    \end{tabular}   
    
\end{resume}
\end{document}